Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-01-13 template.tex
oof ... trying to solve the final integral

\mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}

@@

R_a(f) &= \frac{R_0}{2\pi j} \frac{1}{f-z} \\
z &= f_0 + \frac{j\gamma}{2\pi}

@@

The Fourier transform $S(f)$ is given by Eq. \ref{eq:spec}.  Inserting the spectra into Eq. \ref{eq:midway} and taking the inverse Fourier transform should give $r_a(t) * s_a(t)$.  Note the inverse transform integral is only over positive frequencies, due to the $1+\sgn(f)$ factor.  Introducing the time derivative removes a factor of $(2\pi j f)$ from the numerator of the integrand.  The result is

@@

r_a(t) * s_a(t) = \\ -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{d}{dt} \int_0^\infty \frac{e^{2\pi j ft} e^{-\frac{1}{2}\left(\frac{f}{\sigma_f}\right)^2}}{f-z}df

@@

Completing the square in the exponent, and letting $x = t/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find

@@

r_a(t) * s_a(t) &= -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{dI_1}{dt} \\
I_1 &= e^{-x^2} \int_0^\infty \frac{e^{-(y-j x)^2}}{y-z} dy

@@

The time derivative can be switched to a derivative with respect to $x$:

@@

\boxed{
r_a(t) * s_a(t) = -j \frac{R_0 E_0 \sigma_t^2}{\sqrt{\pi}} \frac{dI_1}{dx}}
Evaluating the derivative $dI_1/dx$ gives
\frac{dI_1}{dx} = 2j e^{-x^2} \int_0^{\infty} \frac{y e^{-(y-jx)^2}}{y-z}dy + 2 x I_1 - 2 x I_1
The final two terms cancel, and the result is
\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I_2(x,z)} \\
\Aboxed{I_2(x,z) &= \int_0^{\infty} \frac{y e^{-(y-jx)^2}}{y-z} dy}
\item Note that $I_2(x,0)$ has an exact solution:
I_2(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
I_2(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)
However, approximating $I_2(x,z) \approx I_2(x,0)$ drops the dependance on $\gamma$ and $f_0$.  This suggests expanding $I_2(x,z)$ in a Taylor series about $z=0$:
I_2(x,z) &\approx I_2(x,0) + \sum_{n=1}^{\infty} z^n I_3(x,n) \\
I_3(x,n) &= \int_0^{\infty} y^{-n} e^{-(y-jx)^2} dy \\
I_3(x,n) &= \int_0^{\infty} y^{-n} e^{(x+jy)^2} dy
For example, when the lower limit is restricted from 0 to just $z$, the term $I(0,1)$ is
I(0,1) = \int_z^{\infty} y^{-1} e^{-y^2} dy = \frac{1}{2}E_1(z)

>>>>

mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}

@@

R_a(f) &= \frac{R_0}{2\pi j} \frac{1}{f-z_0} \\
z_0 &= f_0 + \frac{j\gamma}{2\pi}

@@

The Fourier transform $S(f)$ is given by Eq. \ref{eq:spec}.  Inserting the spectra into Eq. \ref{eq:midway} and taking the inverse Fourier transform should give $r_a(t) * s_a(t)$.  Note the inverse transform integral is only over positive frequencies, due to the $1+\sgn(f)$ factor.  Introducing the time derivative removes a factor of $(2\pi j f)$ from the numerator of the integrand.  Note also that it is prudent to consider the signal $s(t)$ shifted by a $t_0$, to ensure the entire signal is convolved with $r(t)$.  For time-shifts, the Fourier transform responds like:
\mathcal{F}\left\lbrace s(t-t_0)\right\rbrace = e^{-2\pi f t_0} S(f)
The result is

@@

r_a(t) * s_a(t) = \\ -j \sqrt{\frac{2}{\pi}} R_0 E_0 \sigma_t^3 \frac{d}{dt} \int_0^\infty \frac{e^{2\pi j f(t-t_0)} e^{-\frac{1}{2}\left(\frac{f}{\sigma_f}\right)^2}}{f-z}df

@@

Completing the square in the exponent, and letting $x = (t-t_0)/(\sqrt{2}\sigma_t)$, $y = f/(\sqrt{2}\sigma_f)$, and $z \to f_0/(\sqrt{2}\sigma_f)+j \gamma/(2\pi\sqrt{2}\sigma_f)$, we find
r_a(t) * s_a(t) = \\ -\frac{j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \left(e^{-x^2} \int_0^{\infty} \frac{e^{(x+jy)^2}}{y-z_0} dy \right)
Evaluating the derivative gives

@@

\Aboxed{r_a(t) * s_a(t) &= \frac{2R_0 E_0 \sigma_t^2}{\sqrt{\pi}} e^{-x^2} I(x,z_0)} \\
\Aboxed{I(x,z_0) &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy}

@@

\item Note that $I(x,0)$ has exact solutions:
I(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
I(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)
However, approximating $I(x,z_0) \approx I(x,0)$ drops the dependance on $\gamma$ and $f_0$.  Voigt or Faddeeva functions can be introduced, if only the denominator was even in $y$.  This suggests rationalizing the denominator:

@@

\frac{1}{y-z_0} = \frac{\frac{f-f_0}{\sqrt{2}\sigma_f} - \frac{j\gamma}{2\pi\sqrt{2}\sigma_f}}{\frac{(f-f_0)^2}{2\sigma_f^2} + \frac{\gamma^2}{4\pi^2 2\sigma_f^2}}
